\huge Tor's Usability for Censorship Circumvention

### 2016-04-30 pets2017-paper/pets2017-paper.tex
restructure redesign section and flip ordering in goals/evaluation section.

\begin{enumerate}
    \item {\bfseries Task completion rate:} What percentage of users can successfully connect to Tor in a given condition.
    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
\end{enumerate}

A heuristic evaluation is based on standards
in the user interface design community. We draw from Jacob Nielsen's ten heuristics~\cite{nielsen1994heuristic}
to form the following heuristic evaluation criteria: \\

\begin{enumerate}
    \item  {\bfseries Visibility of system status:} There is feedback on system state is and what the system is doing. 
    \item  {\bfseries Error management:}  Errors are in plain language and offers a solution. 
    \item  {\bfseries Understandable language:} Users are able to understand the text and concepts mentioned in the interface. 
\end{enumerate}

@@

% E1
% (Representative of countries such as France and Australia.)
% E2 
% (Representative of countries such as Tunisia.)
% E3
% (Representative of countries such as China and Syria.)

@@

From the results of our qualitative user study, we see that many users struggle with the configuration process. 
The Tor Browser configuration interface does not adequately meet our criteria from Section~\ref{sec:goals} of
managing errors gracefully, communicating in understandable language, and giving  users feedback on system state. 
We rate the severity of each issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\

\begin{itemize}
\item {\bfseries Major Problem:} Error messages do not express errors in plain language nor offer solutions. 
\item {\bfseries Major Problem:} The concepts mentioned in the interface and the questions that users are required to answer are too technical for the average user. 
\item {\bfseries Minor Problem:} The configuration is not visible to the users before they attempt to connect or while they are connecting to the Tor network.
 \end{itemize}

@@

To address these problems, we made the following three changes to the configuration interface:  \\

\begin{enumerate}
\item {\bfseries Added instructions on what to try next on errors.} When an error occurs, text advice on what to try next is shown to the user. The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy. 
\item {\bfseries Reduced the overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process. Since users generally could not understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option. 
\item {\bfseries Added system status visibility.} Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings. The same information is shown on the progress screen while the connection is in progress.
\end{enumerate}

Other changes improve empirical goals from Section~\ref{sec:goals}: task completion rate, time to completion, and safety for high-risk users. Items 5 and~6 improve task completion; 7 and~8 reduce time to completion; and 9 and~10 build users' mental models of censorship circumvention and the network components involved. Users retain full control of the configuration process.\\

\begin{enumerate}
\setcounter{enumi}{3}
\item {\bfseries Added guidance on choosing to connect or configure.} We labeled the configure option specifically for user in heavily censored situations, to urge users to not assume that a website censorship necessitates configuration.
\item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work.

\item {\bfseries Eliminated technical questions.}  We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer. This are two fewer screens in the revised interface. 
\item {\bfseries Added auto-detection of proxies.} In principle, the interface can guess whether a proxy is needed by scanning the operating system configuration. This purely local detection does not carry the potential risks of network probing and should be safe even for at-risk users. (In our experiment, we simulated the auto-detection by hard-coding the fact that a proxy was not required.)

\item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen. Previously, proxies were put after bridge configuration because only a small fraction of users require proxies. With auto-detection, configuring a proxy before a bridge burdens users less than before.
\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network. This aligns with the mental model we are trying to build in the user. As connections are made with each component, the progress bar displays a green check, giving immediate feedback to the user. For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network. Upon failure, users can see which components have succeeded and which have failed.
\end{enumerate}

>>>>

\begin{enumerate}
    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
    \item {\bfseries Task completion rate:} What percentage of users can successfully connect to Tor in a given condition.
\end{enumerate}

@@

@@

Many users struggle with the configuration process. Our changes to the configuration interface address the causes for these issues. These underlying causes are:\\

\begin{enumerate}
\item {\bfseries Users do not know what to do.} Participants did not know the difference between a direct connection and an indirect connection to the Tor network or the difference between bridges, pluggable transports, and proxies. Participants did not know how to configure these network components without any additional instructions. 
\item {\bfseries User feedback is too technical, missing, or misleading.} Participants did not understand the error messages, log lines, and other text in the interface. Participants did not know when they failed, since certain mistakes do not trigger error warnings or timeouts (i.e. a syntactically correct but invalid proxy). Participants assumed they were not making progress, due to the progress bar not giving feedback on subsequent attempts. 
\item {\bfseries Users do not understand censorship circumvention cues.} Participants did not understand how censorship worked and what would circumvent censorship in their environment, despite adequate evidence that signals what components are necessary and unnecessary. A working connection to the Internet did signal to participants that they did not need a proxy; a blocked website did not translate to a blocked domain name; a failed direct connection did not equate to a blocked Tor relay.
 \end{enumerate}

@@

To help users know what to do, we made the following changes:\\

\begin{enumerate}
\item {\bfseries Added instructions on what to try next on errors.} When an error occurs, text advice on what to try next is shown to the user. The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy. 
\item {\bfseries Added guidance on choosing to connect or configure.} We labeled the configure option specifically for user in heavily censored situations, to urge users to not assume that a website censorship necessitates configuration.
\item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work. 
\end{enumerate}

To address too technical, missing, or misleading feedback, we made the following changes:\\ 
\begin{enumerate}
\setcounter{enumi}{3}
\item {\bfseries Progress bar feedback is accurate.}  We fixed the bug that caused the progress bar to not update on subsequent attempts. What users now see on the progress bar reflects the reality of the progress. 
\item {\bfseries Made the interface text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process. Since users generally could not understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option. 
\item {\bfseries Added system status visibility.} Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings. The same information is shown on the progress screen while the connection is in progress. We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network. This aligns with the mental model we are trying to build in the user.
\end{enumerate}

To help clarify with interacting network components with censorship circumvention, we made the following changes:\\

\begin{enumerate}
\setcounter{enumi}{6}
\item {\bfseries Eliminated technical questions.}  We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer. This are two fewer screens in the revised interface. 
\item {\bfseries Added auto-detection of proxies.} In principle, the interface can guess whether a proxy is needed by scanning the operating system configuration. This purely local detection does not carry the potential risks of network probing and should be safe even for at-risk users. (In our experiment, we simulated the auto-detection by hard-coding the fact that a proxy was not required.)
\item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen. Previously, proxies were put after bridge configuration because only a small fraction of users require proxies. With auto-detection, configuring a proxy before a bridge burdens users less than before.
\end{enumerate}
